%----------------------------------------------------------------
%
%  File    :  survey-browsers.tex
%
%  Author  :  Keith Andrews, IICM, TU Graz, Austria
% 
%  Created :  27 May 1993
% 
%  Changed :  16 Nov 2010
% 
%----------------------------------------------------------------


\chapter{HTML Tables}

\label{HTML5 Tables}

In case of having a lot of data to display, or data which is better of in a grid, HTML tables
are the best solution available. Before, tables have been used mostly for the layout of 
HTML web-sites and it is not a good practice to do so, mainly because of two things:


$\bullet$ Semantically it is wrong

$\bullet$ Tables aren't as adaptable and flexible as divs'

\section{Structure of tables}

The basic structure of an HTML table starts with the \textit{<table>} tag. It is the starting
point for constructing a table. Now, HTML tables consist of columns and rows, like normal
tables. For rows, the tag  \textit{<tr>} is used, whereas for table header \textit{<th>} tag
is used. Normally, table headers are positioned in the center and are bold. For table cells
\textit{<td>} tag is used [7]. 

\begin{lstlisting}[%
    language = CSS, 
    xleftmargin=0cm,              % no extra margins for floats
    xrightmargin=0cm,             % no extra margins for floats
    language=biblatex,
    basicstyle=\footnotesize\ttfamily,
    frame=shadowbox,
    numbers=left,
    label=list:BibACMIEEE,
    ,
]
    % An example of an HTML Table which demonstrates information about cars:
    <!DOCTYPE html>
<html>
<head>
	<title>Best Cars 2019</title>
</head>
<body>
<table class="table table-bordered table-hover table-condensed">
	<thead>
		<tr>
			<th title="Field #1">Car</th>
			<th title="Field #2">Manufacturer</th>
			<th title="Field #3">Engine Size</th>
			<th title="Field #4">Cylinders</th>
			<th title="Field #5">Horsepower</th>
			<th title="Field #6">Torque</th>
			<th title="Field #7">Compresion Ratio</th>
			<th title="Field #8">Miles per gallon</th>
			<th title="Field #9">Price</th>
		</tr>
	</thead>
	<tbody>
		<tr>
			<td>2019 Acura RDX</td>
			<td>Acura</td>
			<td>2.00L</td>
			<td align="right">4</td>
			<td align="right">272</td>
			<td align="right">280</td>
			<td>9.8:1</td>
			<td align="right">28</td>
			<td>€33,600.00</td>
		</tr>
		<tr>
			<td>2019 Ford Ranger</td>
			<td>Ford</td>
			<td>2.30L</td>
			<td align="right">4</td>
			<td align="right">270</td>
			<td align="right">310</td>
			<td>10.0:1</td>
			<td align="right">21</td>
			<td>€21,800.00</td>
		</tr>
	</tbody>
</table>

</body>
</html>
    
\end{lstlisting}

Now, there exist some other tags which we can use for HTML5 tables:

$\bullet$ <thead> - Table header, it is used to point out single or multiple rows 
of a table, which don't contain table data but column labels [8].

$\bullet$ <tbody> - Table body, it is used to point out <tr> elements. Position this tag
always after <thead>, but it can also come after or before <tfoot> [8].

$\bullet$ <tfoot> - Table footer, it is used to point out single or multiple <tr> elements
where those elements are presenting an overview  of the data in the table [8]. 

$\bullet$ <caption> - Table caption, as the name already says, can be used to specify table caption.
Can be put on the bottom of the CSS document.

$\bullet$ <col> - While using col and some other keyword, for example, align, we can direct
the alignment of text in the table. There are other keywords with which we can adjust colors, width
and many other things of table columns.  

\section{Responsive Tables}



\subsection{Layered}

\subsection{Radial}





\section{Space-Filling Hierarchy Browsers}

\subsection{Layered}

\subsection{Radial}

\subsection{Inclusive}

\subsection{Overlapping}






\section{Evaluating Hierarchy Browsers}

\subsection{Formative Studies}

\subsection{Comparative Studies}


