%----------------------------------------------------------------
%
%  File    :  survey-recc.tex
%
%  Author  :  Mirza Kabiljagic, Stefan Rajinovic, Aleksandar Stojicic,
%             Inti Gabriel Mendoza Estrada
%
%  Created :  27 May 20xx
%
%  Changed :  4 Dez 2019
%
%----------------------------------------------------------------



\chapter{HTML Tables}

\label{HTML5 Tables}

In case of having too much data to display, or data which is inherently better in a grid, HTML tables
are the best solution available. Before, tables have been used mostly for the layout of
HTML websites (and is now an example of bad website development pracices) mainly due to two reasons:
\begin{itemize}
    \item[--] Semantically, it is wrong.
    \item[--] Tables aren't as adaptable and flexible as divs'
\end{itemize}

\section{Structure of Tables}

The basic structure of an HTML table starts with the \textit{<table>} tag. It is the starting
point for constructing a table. Now, HTML tables consist of columns and rows, like normal
tables. For rows, the tag  \textit{<tr>} is used, whereas for table header \textit{<th>} tag
is used. Normally, table headers are positioned in the center and are bold. For table cells
\textit{<td>} tag is used \parencite{AdamWood}.

\begin{lstlisting}[%
    language = HTML,
    xleftmargin=0cm,              % no extra margins for floats
    xrightmargin=0cm,             % no extra margins for floats
    language=biblatex,
    basicstyle=\footnotesize\ttfamily,
    frame=shadowbox,
    numbers=left,
    label=list:Structure,
    ,
]
    % An example of an HTML Table which demonstrates information about cars:
    <!DOCTYPE html>
<html>
<head>
	<title>Best Cars 2019</title>
</head>
<body>
<table class="table table-bordered table-hover table-condensed">
	<thead>
		<tr>
			<th title="Field #1">Car</th>
			<th title="Field #2">Manufacturer</th>
			<th title="Field #3">Engine Size</th>
			<th title="Field #4">Cylinders</th>
			<th title="Field #5">Horsepower</th>
			<th title="Field #6">Torque</th>
			<th title="Field #7">Compresion Ratio</th>
			<th title="Field #8">Miles per gallon</th>
			<th title="Field #9">Price</th>
		</tr>
	</thead>
	<tbody>
		<tr>
			<td>2019 Acura RDX</td>
			<td>Acura</td>
			<td>2.00L</td>
			<td align="right">4</td>
			<td align="right">272</td>
			<td align="right">280</td>
			<td>9.8:1</td>
			<td align="right">28</td>
			<td>€33,600.00</td>
		</tr>
		<tr>
			<td>2019 Ford Ranger</td>
			<td>Ford</td>
			<td>2.30L</td>
			<td align="right">4</td>
			<td align="right">270</td>
			<td align="right">310</td>
			<td>10.0:1</td>
			<td align="right">21</td>
			<td>€21,800.00</td>
		</tr>
	</tbody>
</table>

</body>
</html>

\end{lstlisting}

Now, there exist more tags which can be used for HTML5 tables:
\begin{itemize}
    \item[--] $<$\texttt{thead}$>$ - Table header, it is used to point out single or multiple rows
of a table, which do not contain table data but column labels \parencite{ChrisCoyier}.

    \item[--] $<$\texttt{tbody}$>$ - Table body, it is used to point out $<$\texttt{tr}$>$ elements. Position this tag
always after $<$\texttt{thead}$>$, but it can also come after or before $<$\texttt{tfoot}$>$ \parencite{ChrisCoyier}.

    \item[--] $<$\texttt{tfoot}$>$ - Table footer, it is used to point out single or multiple $<$\texttt{tr}$>$ elements
where those elements are presenting an overview  of the data in the table \parencite{ChrisCoyier}.

    \item[--] $<$\texttt{caption}$>$ - Table caption, as the name already says, can be used to specify table caption.
Can be put on the bottom of the CSS document.

    \item[--] $<$\texttt{col}$>$ - While using col and some other keyword, for example, align, it is possible direct
the alignment of text in the table. There are other keywords whom can be used to adjust colors, width
and many other things of table columns.
\end{itemize}
